### 2017-11-17 monograph/thesis/chapters/beautifiers.tex
Created the Code Beautifying section on motivation.tex
Created the reference Tracking Changes, trackingChanges.
Created some weblink references/footnotes.

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\chapter{Source Code Beautifiers}

    Below there are some basic formatting rules for illustration:

    \medskip
    \begin{bluebox}
    \begin{enumerate}[nosep,nolistsep]
        \item Add new lines after `\{' and before `\}
        \item Add new lines before `\{'
        \item Remove empty lines
        \item Add comment lines before function
        \item Add new lines after `;'
        \item Add new lines after `\}'
        \item Remove new lines
        \item Reduce whitespace
        \item Put the code again in the input box above after submit
    \end{enumerate}
    \end{bluebox}
    \vspace{-4mm}\begin{flushright}\textcite{prettyPrinter}\end{flushright}

@@

    \citeonline{annotationAssistant},
    \citeonline{codePlagiarismDetection},
    \citeonline{softwarePortfolio},
    \citeonline{legacyAssets},
    \citeonline{massMaintenance},
    \citeonline{prettyPrinting},
    \citeonline{architectureFormatting},
    \citeonline{independentFramework},
    \citeonline{programIndentation},
    \citeonline{industrialApplication},
    \citeonline{toolsForProjectManagement},
    \citeonline{codeClassification},
    \citeonline{codeScanningPatterns},
    \citeonline{debuggingIntoExamples},
    \citeonline{programUnderstanding},
    \citeonline{documentingAndSharingKnowledge},
    \citeonline{autofoldingForSourceCode},
    \citeonline{learningSupportSystem},
    \citeonline{syntaxHighlightingInfluencing},
    \citeonline{improvingCodeReadability},
    \citeonline{howNovicesRead},
    \citeonline{theRoleOfMethodChains},
    \citeonline{codeComprehensionComparedToOO},
    \citeonline{enhancingLegacySoftwareSystemAnalysis},
    \citeonline{moldableCodeEditor},
    \citeonline{blindAndSightedProgrammers},
    \citeonline{pushdownAutomata}

>>>>

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\label{source_code_beautifiers}
\chapter{Source Code Beautifiers}

    Below there are some basic formatting rules for
    illustration:\footnote{\url{https://www.python.org/dev/peps/pep-0008/#should-a-line-break-before-or-after-a-binary-operator}}

    \medskip
    % \begin{bluebox}
    \begin{enumerate}[nosep,nolistsep]
        \item Add new lines after `\{' and before `\}
        \item Add new lines before `\{'
        \item Remove empty lines
        \item Add comment lines before function
        \item Add new lines after `;'
        \item Add new lines after `\}'
        \item Remove new lines
        \item Reduce whitespace
        \item Fix bad indentation
    \end{enumerate}
    % \end{bluebox}
    \vspace{-4mm}\begin{flushright}\textcite{prettyPrinter}\end{flushright}

    Mostly,
    code formatting is recuded into this set of changes.

@@

    \citeonline{annotationAssistant},
    \citeonline{codePlagiarismDetection},
    \citeonline{softwarePortfolio},
    \citeonline{legacyAssets},
    \citeonline{massMaintenance},
    \citeonline{prettyPrinting},
    \citeonline{architectureFormatting},
    \citeonline{independentFramework},
    \citeonline{programIndentation},
    \citeonline{industrialApplication},
    \citeonline{toolsForProjectManagement},
    \citeonline{codeClassification},
    \citeonline{codeScanningPatterns},
    \citeonline{debuggingIntoExamples},
    \citeonline{programUnderstanding},
    \citeonline{documentingAndSharingKnowledge},
    \citeonline{autofoldingForSourceCode},
    \citeonline{learningSupportSystem},
    \citeonline{syntaxHighlightingInfluencing},
    \citeonline{improvingCodeReadability},
    \citeonline{howNovicesRead},
    \citeonline{theRoleOfMethodChains},
    \citeonline{codeComprehensionComparedToOO},
    \citeonline{enhancingLegacySoftwareSystemAnalysis},
    \citeonline{moldableCodeEditor},
    \citeonline{blindAndSightedProgrammers},
    \citeonline{pushdownAutomata},
